Retrofitting Effect Handlers onto OCaml

### 2020-11-20 retro-concurrency.tex
Reworked conclusion with avsm

We have presented the design and implementation of effect handlers aimed at
retrofitting them onto the large body of existing OCaml code. Our design walks
the tightrope of maintaining compatibility (e.g. for profiling and debuggers
and negligible overheads for existing programs) and also demonstrating good
performance and usability for new OCaml code that takes advantage of effect
handlers. Our evaluation shows that we have achieved our goal of balancing
compatibility with the introduction of effect handlers for mainstream OCaml
programming.

>>>>

Our design for effect handlers in OCaml walks the tightrope of maintaining
compatibility (for profiling, debuggers and negligible overheads for existing
programs), while unlocking the full power of non-local control flow constructs.
Our evaluation shows that we have achieved our goal: we retain compatibility
with a surprisingly low performance overhead for sequential code that preserves
the spirit of ``fast exceptions'' that has always characterised OCaml
programming. We believe that the introduction of first-class fibres and effects
into OCaml -- along with a parallel runtime~\cite{Sivaramakrishnan20} -- will
open OCaml to highly task-parallel applications with minimal hit to sequential
performance.
